---
title: "hw 2"
output: pdf_document
date: "2022-10-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(RColorBrewer)
```
```{r}
setwd("~/Documents/GitHub/stats100")
```

```{r}
colors<- read.csv("colors.csv")
colors
```
## A. Plot a barplot of the eye color of the subjects. What color is the least common?
```{r}
colors %>%
  ggplot(aes(x=Eye, fill=Eye))+
  geom_bar()+
  labs(x="Eye Color", y="Frequency")
```
## B. Plot a two category barplot of the subjects, using sex and eye color. Comparing men and women, who has a higher probability of brown eyes?
```{r}
colors %>%
  ggplot(aes(x=Eye, fill=Sex))+
  geom_bar(position="dodge")+
  labs(x="Eye Color", y="Frequency", title = "Eye Color By Sex")
```
## C. Plot a mosaic plot of sex and eye color. Are there more males or females in the study? Do males or females tend to have a higher probability of blue eyes? What eye color is least common for males?
```{r}
estable <-table(colors$Sex, colors$Eye)
estable
```

```{r}
mosaicplot(estable, main = "Eye Colors By Sex", color = brewer.pal(4, "BrBG"))
```
```{r}
colors %>%
  ggplot(aes(x=GPA))+
  geom_histogram(binwidth = 0.1, color = "limegreen", fill= "mediumpurple1")
```
```{r}
colors %>%
  ggplot(aes(x=GPA, y=Sex, fill=Sex))+
  geom_boxplot()
```
```{r}
colors %>%
  ggplot(aes(x=GPA, y=Eye, fill=Eye))+
  geom_boxplot()
```

