---
title: "hw 6"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)
```
```{r}
setwd("~/Documents/GitHub/stats100")
```

```{r}
library(tidyverse)
library(stats)
library(asbio)
library(tcltk)
```

#1
```{r}
iqq<- read.csv("IQ.csv")
iqq
```
On Canvas under Files you will find a dataset IQ.csv. It
has two columns, the first of which denotes what major
a student is from (A, B, or C). The second is the IQ
measured by the Stanford–Binet Intelligence Scales. The
goal is to determine if this IQ measure differs between
majors.
(a) Calculate the family-wise (simultaneous, Bonfer-
roni) 95% confidence intervals for (muA-muB), (muA-
muC), and (muB -muC), assuming you will make k = 3
total confidence intervals.
```{r}
summary(iqq)
```

```{r}
qt(1-0.05/(2*3), 45-3)
```
```{r}
Ybar = aggregate(iq ~ group, data = iqq, mean)$iq
ni = aggregate(iq ~ group, data = iqq, length)$iq
```

```{r}
the.model = lm(iq ~ group, data = iqq)
ANOVA.table = anova(the.model)
mse = ANOVA.table[2,3] #ms(within)
```

```{r}
alpha = 0.05
I = 3 # number of groups 
k = choose(I, 2)
n. = sum(ni) #total sample size

t_ag = qt(1- alpha/(2*k), df = n. - k) #t percentile
```
```{r}
# 4. Construct the bonferroni CIs

BON12 = c(Ybar[1] - Ybar[2] - t_ag*sqrt(mse*(1/ni[1] + 1/ni[2])), 
          Ybar[1] - Ybar[2] + t_ag*sqrt(mse*(1/ni[1] + 1/ni[2])))
BON13 = c(Ybar[1] - Ybar[3] - t_ag*sqrt(mse*(1/ni[1] + 1/ni[3])), 
          Ybar[1] - Ybar[3] + t_ag*sqrt(mse*(1/ni[1] + 1/ni[3])))
BON23 = c(Ybar[2] - Ybar[3] - t_ag*sqrt(mse*(1/ni[2] + 1/ni[3])), 
          Ybar[2] - Ybar[3] + t_ag*sqrt(mse*(1/ni[2] + 1/ni[3])))
```
```{r}
# 5. We could calculate the two side p-value
pvalue12 = 2*pt(abs(Ybar[1] - Ybar[2])/sqrt(mse*(1/ni[1] + 1/ni[2])), df = n.-k, lower.tail = F)
pvalue13 = 2*pt(abs(Ybar[1] - Ybar[3])/sqrt(mse*(1/ni[1] + 1/ni[3])), df = n.-k, lower.tail = F)
pvalue23 = 2*pt(abs(Ybar[2] - Ybar[3])/sqrt(mse*(1/ni[2] + 1/ni[3])), df = n.-k, lower.tail = F)
allpvalues = c(pvalue12, pvalue13, pvalue23)
```

```{r}
BON_all = rbind(BON12, BON13, BON23)
all.result = cbind(BON_all, allpvalues)
rownames(all.result) = c("A vs. B", "A vs. C", "B vs. C")
colnames(all.result) = c("Lower", "Upper", "P-value")
knitr::kable(all.result)
```


(b) What is the largest significant difference in averages
suggested by all of the confidence intervals? (This
should be one number).
A vs. C 
```{r}
18.028046-6.771954
```


(c) What is the smallest significant difference in aver-
ages suggested by all of the confidence intervals?
(This should be one number).
B vs. C
```{r}
17.961379-6.705288	
```


(d) What two majors were the most significantly differ-
ent according to the confidence intervals?
A and B

#2

```{r}
beanz<- read.csv("beans.csv")
beanz
```
(a) Find the test statistic.

```{r}
beantable<- table(beanz)
beantable
```

```{r}
beantest<- chisq.test(beantable, correct = F)
beantest
```
Answer = 8.1796
(b) Find the p-value.
Answer = 0.04244

(c) Did you reject or fail to reject the null if alpha = 0.05?
Answer p<a so we can reject

(d) Which bean plant(s) did the weevils prefer more
than expected if the null was true?
```{r}
beantable-beantest$expected
```
Answer = Northern
(e) What category contributed most to the value of the
test-statistic?
```{r}
beantest$residuals^2
```
Answer = Northern
#3
```{r}
blood<- read_csv("blood.csv")
blood
```

(a) State the appropriate null for testing if having this
particular disease is independent of blood type and
alternative hypothesis for testing if having this par-
ticular disease is independent of blood type.

Null:Disease is not independent from blood type
Alt: Disease is independent from blood type

(b) Find the test-statistic.
```{r}
bloodtable<- table(blood$Type, blood$Disease)
bloodtable
```
```{r}
bloodtest<- chisq.test(bloodtable, correct = F)
bloodtest
```
Answer = 10.654
(c) Find the p-value.
Answer = 0.01375

(d) State your conclusion in terms of the problem, as-
suming alpha = 0.01.

p>a so we cannot reject. We cannot say for sure that they are independent

(e) Were blood type A individuals more or less likely to
have the disease than what we expected if the null
was true?
```{r}
bloodtest$observed - bloodtest$expected
```
Answer = Less likely

(f) Were blood type O individuals more or less likely to
have the disease than what we expected if the null
was true?

Answer = More likely

(g) Which group contributed most to the value of the
test-statistic?
```{r}
bloodtest$residuals^2
```

Answer = AB