---
title: "hw 4"
output: pdf_document
date: "2022-10-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
setwd("~/Documents/GitHub/stats100")
```

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(stats)
```
Column 1: height: The height of the student.
Column 2: hsGPA: The high school GPA of the student.
Column 3: pulse: The pulse rate of the student when
measured in class.

```{r}
students <- read.csv("student.csv")
students
```
```{r}
summary(students)
```



#(a) Using R, find the 95% confidence interval for theaverage students height. (Confidence interval for a mean)
```{r}
t.test(students$height, conf.level = 0.95)
```
#(b) What is the highest average height you expect a student to have, based on the confidence interval from (a)?

The upper bound of the confidence interval, which is 68.5639

#(c) Using R, find the 99% confidence interval for the average students pulse.
```{r}
t.test(students$pulse, conf.level = 0.99)
```
#(d) What is the lowest average pulse you expect a student to have, based on the confidence interval from (c)?

The lower bound of the confidence interval, which is 71.5894