---
title: "hw 5"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
setwd("~/Documents/GitHub/stats100")
```

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(stats)
```


```{r}
drp<- read.csv("drp.csv")
drp
```
A treatment class of 21
third-grade students participated in these activities for
eight weeks, and a control class of 23 third-graders fol-
lowed the same curriculum without the activities. After
the eight-week period, students in both classes took a
Degree of Reading Power (DRP) test which measures
the aspects of reading ability that the treatment is de-
signed to improve.
The first column is the group (treatment or control), and
the second is the DRP score (the higher the better).

(a) Find the 95% confidence interval for the difference
in average DRP score.

```{r}
controlt<- drp %>%
  filter(Treatment == "Control") %>%
  summarise(Treatment, Response)
controlt
```
```{r}
treatedt<- drp %>%
  filter(Treatment == "Treated") %>%
  summarise(Treatment, Response)
treatedt
```

```{r}
t.test(controlt$Response, treatedt$Response, conf.level = 0.95)
```
Answer = (-18.67588, -1.23302)

(b) If the experimenter is interested in if the treatment
group has a higher average than the control group,
find the test-statistic.

```{r}
t.test(controlt$Response, treatedt$Response, alternative = "less")
```





