---
title: "hw 5"
output: pdf_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
setwd("~/Documents/GitHub/stats100")
```

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(stats)
```


```{r}
drp<- read.csv("drp.csv")
drp
```
A treatment class of 21
third-grade students participated in these activities for
eight weeks, and a control class of 23 third-graders fol-
lowed the same curriculum without the activities. After
the eight-week period, students in both classes took a
Degree of Reading Power (DRP) test which measures
the aspects of reading ability that the treatment is de-
signed to improve.
The first column is the group (treatment or control), and
the second is the DRP score (the higher the better).

(a) Find the 95% confidence interval for the difference
in average DRP score.

```{r}
controlt<- drp %>%
  filter(Treatment == "Control") %>%
  summarise(Treatment, Response)
controlt
```
```{r}
treatedt<- drp %>%
  filter(Treatment == "Treated") %>%
  summarise(Treatment, Response)
treatedt
```

```{r}
t.test(controlt$Response, treatedt$Response, conf.level = 0.95)
```
Answer: (-18.67588, -1.23302)

(b) If the experimenter is interested in if the treatment
group has a higher average than the control group,
find the test-statistic.

```{r}
t.test(controlt$Response, treatedt$Response, alternative = "less")
```
Answer: -2.3109

(c) If the experimenter is interested in if the treatment
group has a higher average than the control group,
find the p-value.

Answer: 0.01319

(d) Do we fail to reject or reject the null hypothesis if
a = 0.05?

Answer: 0.01319<0.05 so p<a and we can reject null

IQ.csv has two
columns, the first of which denotes what major a stu-
dent is from (A, B, or C). The second is the IQ measured
by the Stanford–Binet Intelligence Scales. The goal is to
determine if this IQ measures differs on average between
majors.

```{r}
iqdf<- read_csv("IQ.csv")
iqdf
```
```{r}
iqmodel<- lm(iqdf$iq~iqdf$group)
iqmodel
```
```{r}
anova(iqmodel)
```

(a) Find the value of the F test-statistic.
Answer: F stat= 20.016

(b) Find the p-value of the test.
Answer: P-value= Pr(>F)=7.843e-07

c) Do we fail to reject or reject the null hypothesis?
(Choose your own a)
Answer: If a=0.001 then p-value is less than that it, and p<a so we can reject the null

(d) State your conclusion in terms of the problem.
Answer: Rejection of null means that average IQ does not vary by major

